Graphical representation example: Alternative interpretations

### 2023-11-23 notebooks/Graphical_representation_alternatives.Rmd
Versions explanation of the plot in the latent space

>>>>

Unless there is a mistake, we can see that the representation is the same. The
angles seem to be correct, and the computed coordinates seem to be given
"perpendicular" to the latent space axes[^ls-coords]

[^ls-coords]: This seems odd, there may be a mistake in the computation of the
latent space grid. Also, it seems like the coordinates are not correct, even if
they are (apparently) computed perpendicularly to the latent space axes.
